%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,roman]{moderncv}

\moderncvstyle{banking}
\moderncvcolor{black}  
\nopagenumbers{}      

\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage{CJKutf8}                              


\usepackage[scale=0.85]{geometry}
\usepackage{multicol}


\usepackage{import}


\name{Raul}{Vazquez}
\title{Software Engineer}                               
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

  
\setlength{\tabcolsep}{12pt}
\renewcommand{\labelitemi}{\small$\bullet$}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-18mm}
\begin{center}
\begin{tabular}{ c c c }
 \faMobile\enspace Skype: rvazquezg72 & \faEnvelopeO\enspace rvazquezglez@acm.org %& \faMapMarker\enspace  Mexico City 
 \\  
\end{tabular}
\end{center}

\section{PROFESSIONAL EXPERIENCE}
{\customcventry{August 2017 - current}{\textbf{Senior Software Engineer}}{Rooam Inc.}{Washington, D.C. (remote)}{}{}}
  {\begin{itemize}
    \item Built and operate systems with a full-cycle approach, from gathering requirements and designing architecture to support live operations and monitoring.
    \item Refactored existing systems to enable users located on different time-zones.
    \item Created an internal system to automatically create and assign incidents to help on-call team.
    \item Implemented integration with third party systems enabling operations on more restaurants.
  \end{itemize}
}

\setlength{\parskip}{0.5em}

{\customcventry{March 2014 - December 2017}{\textbf{Senior Software Engineer}}{Switchfly Inc.}{San Francisco, California (remote)}{}{}}
  {\begin{itemize}
    \item Rescued a payment processing project that was considered sunk and made it usable for all Latin America region.
    \item Became a Subject Matter Expert on loyalty and travel activities modules of the Switchfly platform.
    \item Vetted and groomed requests for change in the requirements funnel.
    \item Designed and implemented new software features while maintaining legacy ones.
    \item Taught other team members on how to write more readable, testable and reusable code.
  \end{itemize}
}

\setlength{\parskip}{0.5em}

{\customcventry{May 2013 - March 2014}{\textbf{Scrum Master, Technical Leader}}{GNP Insurance}{Mexico City, Mexico}{}{}}
  {\begin{itemize}
    \item Lead a team of five, removing impediments, guiding into self-management and extreme programming techniques.
    \item Designed the architecture of new software features for managing insurance policies.
    \item Implemented continuous integration pipelines allowing the team to deliver faster and more often.
  \end{itemize}
}

{\customcventry{September 2012 - February 2013}{\textbf{Technical Leader, Senior Developer}}{SintelTI}{Mexico City, Mexico}{}{}}
  {\begin{itemize}
    \item Lead a team of three to implement a casino like application.
    \item Built a system to unify and manage vital records (birth, marriage, death) across the country for the National Population Registry.
  \end{itemize}
}

% {\customcventry{May 2012 - March 2015}{\textbf{JEE specialist, Instructor}}{TecGurus}{Mexico City, Mexico}{}{}}
%   {\begin{itemize}
%     \item tasks
%   \end{itemize}
% }

\section{EDUCATION BACKGROUND}
{\customcventry{January 2019 - Present}{Master of Computer Science (Data Engineering)}{Arizona State University (ASU)}{Tempe, Arizona (remote)}{}{}}
 
{\customcventry{August 2006 - August 2011}{Bachelor of Computer Systems Engineering (Software Engineering)}{National Polytechnic Institute (IPN)}{Mexico City, Mexico}{}{}}




\section{KEY TECHNICAL SKILLS}


{
Java, Groovy, Kotlin, Scala, Spring Boot, Spring Data, Spring Cloud, PostgreSQL, MongoDB.
}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

\end{document}
